Appendix: Computational Luminance Constancy from Naturalistic Images

### 2018-10-24 Production/Production.tex
david’s comments edited in

We define the computational problem of luminance constancy\footnote{In the literature, the term lightness constancy is generally used to denote color constancy for the special case when stimuli are restricted to be achromatic. This condition does not apply to our work - we consider full spectral variation in the stimuli. We chose the term luminance constancy to denote the generalization from achromatic stimuli. At the same time we acknowledge that we are not studying the full problem of color constancy. Rather, we are studying the estimation of a luminance-based summary of surface spectral reflectance.} as that of estimating the luminous reflectance factor (LRF) of a target object's surface reflectance function.
The LRF is a measure of the overall amount of light reflected by a surface relative to the reference illuminant itself\footnote{LRF is related to albedo, but the concept of albedo does not incorporate the human luminosity function.} \cite{astm1121477}.
Obtaining the LRF from a known surface reflectance function requires two steps.
First, one computes the luminance of the light that would be reflected from the surface under a reference illuminant.
Second, one normalizes the result by the luminance of the reference illuminant itself.
Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance \cite{CIE86}.
Sometimes LRFs are expressed as a percentage.
Here we express LRFs as proportions, so that they take on values between 0 and 1. 
An LRF of 0 means that none of the light from the reference illuminant is reflected from the surface. 
An LRF of 1 means that the luminance of the surface reflectance under the reference illuminant is the same as the luminance of a perfect reflector under that same illuminant.

>>>>

We define the computational problem of luminance constancy\footnote{In the literature, the term lightness constancy is generally used to denote color constancy for the special case when stimuli are restricted to be achromatic. This condition does not apply to our work - we consider full spectral variation in the stimuli. We chose the term luminance constancy to denote the generalization from achromatic stimuli. At the same time we acknowledge that we are not studying the full problem of color constancy. Rather, we are studying the estimation of a luminance-based summary of surface spectral reflectance.} as that of estimating the luminous reflectance factor (LRF) of a target object's surface reflectance function.
The LRF is a measure of the overall amount of light reflected by a surface relative to the reference illuminant itself.\footnote{LRF is related to albedo, but the concept of albedo does not incorporate the human luminosity function. The terminology surrounding LRF and the related concept light reflectance value (LRV) varies somewhat in the literature. Here we follow the definition of LRF given by the \citeNP{astm1121477}.}
Obtaining the LRF from a known surface reflectance function requires two steps.
First, one computes the luminance of the light that would be reflected from the surface under a reference illuminant.
Second, one normalizes the result by the luminance of the reference illuminant itself.
Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance \cite{CIE86}.
Sometimes LRFs are expressed as a percentage.
Here we express LRFs as proportions, so that they take on values between 0 and 1. 
An LRF of 0 means that none of the light from the reference illuminant is reflected from the surface. 
An LRF of 1 means that the luminance of the surface reflectance under the reference illuminant is the same as the luminance of a perfect reflector under that same illuminant.

### 2018-10-24 Production/appendix.tex
editing figures for production
david’s comments edited in

\date{}
\begin{document}
\title{Appendix: Luminance constancy under fixed geometry}

@@

\begin{figure}
\centering
    \begin{subfigure}[b]{0.4 \textwidth}
	\caption{Cone excitations}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/FigureSI/SI_Figure1_a.pdf}
	\label{fig:case1RFs}
    \end{subfigure}   
    \begin{subfigure}[b]{0.4 \textwidth}
	\caption{Normalized contrast}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/FigureSI/SI_Figure1_b.pdf}
	\label{fig:case1RFs}
    \end{subfigure}   
    \caption{{\bf Condition 2 receptive fields:} The first three AMA receptive fields learnt on (a) Cone excitations (b) Normalized contrast.}
\label{fig:Condition1}
\end{figure}

>>>>

\date{}
\begin{document}
\title{Appendix: Computational Luminance Constancy from Naturalistic Images}

@@

\begin{figure}
\centering
    \begin{subfigure}[b]{0.4 \textwidth}
	\caption{Cone excitations}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/FigureSI/SI_Figure1_a.pdf}
	\label{fig:case1RFs}
    \end{subfigure}   
    \begin{subfigure}[b]{0.4 \textwidth}
	\caption{Contrast normalized}
	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/FigureSI/SI_Figure1_b.pdf}
	\label{fig:case1RFs}
    \end{subfigure}   
    \caption{{\bf Condition 2 receptive fields:} The first three AMA receptive fields learnt on (a) Cone excitations (b) Contrast normalized.}
\label{fig:Condition1}
\end{figure}
